%\chapter*{Multiple Choice Math Questions}
\begin{enumerate}










\item How many pounds per day of $100 \%$ chlorine gas are needed to arrive at a dosage of $2 \mathrm{mg} / \mathrm{L}$, when the flow is $8.8 \mathrm{mgd}$ and a zero chlorine demand exists?\\
a. *147\\
b. $1,097.9$\\
c. 1,468\\
d. 211.3\\
e. 417\\
  \item How many pounds per day of $100 \%$ chlorine gas are needed to arrive at a residual of $2.3 \mathrm{mg} / \mathrm{L}$, when the flow is $8.25 \mathrm{mgd}$ and a chlorine demand is $0.35 \mathrm{mg} / \mathrm{L}$ ?\\
a. 21.8\\
c. 27.4\\
e. 812.3\\
b. *182.3\\
d. 158.3\\
  \item When a filter whose surface loading rate is $1,500 \mathrm{gpd} / \mathrm{sq}$.ft. and its size is 400 -sq. $\mathrm{ft}$. Determine the total flow through the filter in gallons per day.\\
a. 0.6\\
c. 7.85\\
e. *600,000\\
b. 375,000\\
d. 3.75\\
  \item Determine the Unit Filter Run Volume of a 15-ft. x 20-ft. filter when it registered 2,000,000 gallons during its run.\\
a. 600\\
c. 989\\
b. 9423\\
d. *6667\\
e. 7200\\
  \item A filter has the dimensions of 15-ft. x 20-ft and a backwash rate of 19.5 gpm/sq.ft. Determine its backwash rise rate in, inches per minute.\\
a. 58.5\\
c. 5.85\\
e. *31.2\\
b. 37\\
d. 81.3\\
  \item Using the Quantity formula $(\mathrm{Q}=\mathrm{AV})$, determine the $\mathrm{Q}$ when $\mathrm{A}=15$ sq. $\mathrm{ft}$. and velocity is $3.3 \mathrm{ft} / \mathrm{sec}$.\\
a. *$49.5 \mathrm{cfs}$\\
c. $19.88 \mathrm{cfs}$\\
e. $4.9 \mathrm{cfs}$\\
b. $495 \mathrm{cfs}$\\
d. $4.545 \mathrm{cfs}$\\
  \item Find the gpm/sq.ft. filtration rate when 6,775,000 gallons were produced in 24-hours through a filter that measures $30-\mathrm{ft} . \mathrm{x} 54-\mathrm{ft}$.\\
a. 0.029\\
c. 2904.2\\
e. 4.18\\
b. 0.29\\
d. *2.9 

\item What is the grain per gallon (gpg) hardness of water that has a total hardness of $228 \mathrm{mg} / \mathrm{L}$ ?\\
a. *14\\
c. 18\\
e. 133.3\\
b. 3898.8\\
d. 39\\
  \item A water tank had a pressure gauge reading of 14 psig on its bottom. Determine the water level in the tank.\\
a. 23.3 feet\\
c. *32.3 feet\\
e. 19.8\\
b. 28.6 feet\\
d. 38.3 feet\\
  \item A tank had a diameter of 22-feet and a pressure of 7.7 psi on its bottom. Determine how many pounds of $65 \%$ calcium hypochlorite (dry powder chlorine) are needed to arrive at a dosage of $1 \mathrm{ppm}$.\\
a. 0.42 pounds\\
b. *$0.65 \mathrm{lbs}$\\
c. $50,302.5$ pounds\\
d. $41.9 \mathrm{lbs}$\\
e. 6.5 lbs\\

\item An iron removal plant processes water with an average iron concentration of 2.5 mg/l. If the iron concentration is 0.01 mg/l after treatment and the total daily pumpage is one million gallons, how many pounds of iron will be removed per day?\\
a. 10.77 pounds\\
a. *20.77 pounds\\
b. 25.77 pounds\\
c. 30.77 pounds\\
d. 35.77 pounds\\
\item A water system bills quarterly at a rate of 25¢/1000 gallons for the first 10,000 gallons, 30¢/1000 gallons for the next 10,000 gallons, 35¢/1000 gallons for all over 20,000 gallons.  If a customer uses 35,000 gallons per quarter, what is the water bill?\\
a. \$ 9.50\\
b. *\$ 10.75\\
c. \$ 12.25\\
d. \$ 12.50\\
e. \$ 13.25\\

\item A ground level storage tank is 25 feet long, 20 feet wide, and 10 feet deep. When the storage tank is completely empty, calculate how many minutes it will take to fill the tank with a pump that has a capacity of 300 gallons per minute.\\
a. 60 minutes\\
b. 100 minutes\\
c. *125 minutes\\
d. 150 minutes\\
e. 200 minutes\\



\item A room measures $12 \mathrm{ft}$ high, 30 ft long, and 17 ft wide. How many cubic feet per minute of air must a blower in an air exchange unit move to completely change the air every 10 minutes?\\
a. 102\\
b. 612\\
c. 1,020\\
d. 6,120\\


\item If a trench is $526 \mathrm{ft}$ long, $4.0 \mathrm{ft}$ wide, and $5.5 \mathrm{ft}$ deep, how many cubic yards of soil were excavated?\\
$$526 \times 4 \times 5.5=\frac{11,572 \mathrm{f}^{3}}{27}=428$$\\

\item If exactly $100 \mathrm{gal}$ of polymer costs $\$ 19.50$, what will $5,500 \mathrm{gal}$ cost, assuming no quantity discount?\\
$$\frac{19.50}{100} \times 5500=1,072.5$$\\

\item What is the velocity of flow in feet per second for an 8.0-in. diameter pipe if it delivers 675 gprax?\\
$$\frac{150}{6.35}$$\\

$$\frac{675}{449}=15 \mathrm{cuft} / \mathrm{s}$$\\

$$\begin{aligned} & 430 \mathrm{ft} / \mathrm{s} \end{aligned}$$\\

\item What should the setting be on a chlorinator in pounds per day if the dosage desired is $2.90 \mathrm{mg} / \mathrm{L}$ and the pumping rate from the well is $975 \mathrm{gpm}$ ?\\
$$\frac{975}{69)^{1}}=1.4 MGD $$\\
$$1.4 \times 8.34 \times 2.90$$\\

\item A treatment plant uses $278 \mathrm{lb} / \mathrm{d}$ of chlorine gas. If the chlorine demand is $0.85 \mathrm{mg} / \mathrm{L}$ and the chlorine residual is $1.50 \mathrm{mg} / \mathrm{L}$, how many million gallons per day are being treated?\\
$$\frac{278}{8.34 \times 2 \times 35}=$$\\
$$\text { dojarge } ;$$\\
$$\begin{aligned}& 0.85+1.50= \\& 2.35 \mathrm{mg} / \mathrm{h}\end{aligned}$$\\

\item A water tank that is $105 \mathrm{ft}$ in diameter needs to be disinfected with a $5.0 \%$ sodium hypochlorite solution. If the tank is to be filled to only a depth of $5.0 \mathrm{ft}$ and the concentration required is $20.0 \mathrm{mg} / \mathrm{L}$, how many gallons of sodium hypochlorite are needed? Assume the sodium hypochlorite solution weighs 8.92 lb/gal.\\
$$\frac{0.323 M G P}{0.323 \times 8.34 \times 20}=$$\\
$$9 / 23 / 19$$\\

\item Convert $8.0 \mathrm{cfs}$ to $\mathrm{gpm}$.\\
a. $1.07 \mathrm{gpm}$\\
$\begin{array}{ll}\text { b. } 64.2 \mathrm{gpm} \\ \text { c. } 480 \mathrm{gpm} & 8 \times 449\end{array}$\\
(e.) $3,436 \mathrm{gpm}$\\

\item Conyert 4,000 gpm to cfs.\\
a.  $8.91 \mathrm{cfs}$\\
b. $66.65 \mathrm{cfs}$\\
c. $499 \mathrm{cfs}$\\
d. $535 \mathrm{cfs}$\\
e. $32,076 \mathrm{cfs}$\\

\item Convert $12 \mathrm{MGD}$ to gpm.\\
a. $0.00833 \mathrm{gpm}$\\
b. $7,200 \mathrm{gpm} \quad 12 \times 700$\\
d. $17,280 \mathrm{gpm}$\\
e. $199,992 \mathrm{gpm}$\\

\item Convert $5.5$ cfs to MGD.\\
a. $0.059 \mathrm{MGD}$\\
b. $0.148$ MGD\\
c. $0.475 \mathrm{MGD}$\\
(64) more Aaumole\\
e. 7,920 MGD\\

\item Convert 45 Acre-feet into million gallons.\\
a. $6.02 \mathrm{Mgal}$\\
b. $1.96 \mathrm{Mgal}$\\
c.  $14.7 \mathrm{Mgal}$\\
d. $45 \mathrm{Mgal}$\\
e. $336.6 \mathrm{Mgal}$\\

\item Convert $6.5$ feet per second into miles per hour.\\
a.  $4.43 \mathrm{mph}$\\
c. $13.3 \mathrm{mph}$\\
d. $106 \mathrm{mph}$\\
e. $266 \mathrm{mph}$\\

\item Convert $3.4$ miles into feet.\\
a. 5,000 feet\\
b. 5,280 feet\\
c. 5,984 feet\\
d. 10,000 feet\\
(e.) 17,952 feet\\
$$=\frac{6.5 / 5280}{1 / 60 \times 60}$$\\
$1 \mathrm{~m} / \mathrm{e}=25$ ft\\

\item Convert $2,250 \mathrm{gpm}$ into MGD.\\
a. 0.054MGD\\
b. $3.24 \mathrm{MGD}$\\
d. $2,250 \mathrm{MGD}$\\
e. 3,240 MGD\\

\item Convert $9.75 \mathrm{MGD}$ into cfs.\\
a.  $15.1 \mathrm{cfs}$\\
b. $37.75 \mathrm{cfs}$\\
c. $113 \mathrm{cfs}$\\
d. $363 \mathrm{cfs}$\\
e. $845 \mathrm{cfs}$\\
$$236 \pi$$\\

\item Convert $1,000,000$ cubic feet into Acre-feet.\\
a. $0.04356 \mathrm{AF}$\\
b. $0.325829 \mathrm{AF}$\\
c. $3.07 \mathrm{AF}$\\
d. $22.96 \mathrm{AF}$\\
e. $172 \mathrm{AF}$\\

\item What is the chlorine residual in a treated water if the dosage is $2.1 \mathrm{mgi1}$ and has a demand of $0.8 \mathrm{mg} / \mathrm{l}$\\
a. $0.8 \mathrm{mg} / \mathrm{l}$\\
b. $1 \mathrm{mg} / \mathrm{l}$\\
c. $\quad 2.1 \mathrm{mg} / !$\\
d. $\quad 2.9 \mathrm{mg} / \mathrm{l}$\\

\item What is the maximum amount of ch1orine gas that can be removed from a 150-lb cylinder in 24 hrs?\\
a. 26 lbs. .\\
b. 40Jbs.\\
c. $75 \mathrm{lbs}$.\\
d. there is no maxim.um\\

\item Bow many gallons would be contained in a circular tank that is $100 \mathrm{ft}$. in diameter and $10 \mathrm{ft}$ deep?\\
a. $\quad 587,0.00$ gallons\\
b. 657,000 gallons\\
c. 1,340,000 gallons\\
d. $\quad 2,349,000$ gallons\\


\item In order to rebuild a manhole, it will be necessary to remove the asphalt from a 35-foot diameter circle in a street. The pavement area involved is:\\
a. $\quad 208 \mathrm{sq. ft}$\\
b. $\quad 241, \mathrm{sq. ft}$\\
c. $\quad 962 \mathrm{sq. ft}$\\
d. $\quad 1125 \mathrm{sq. ft}$\\

\item If the chlorine demand of water is $2.5 \mathrm{mg} / \mathrm{l}$ and you want a residual of $0.5 \mathrm{mg} / \mathrm{l}$, how much chlorine would need to be fed to one million gallons?\\
a. $\quad 25 \mathrm{lbs}$.\\
b. $\quad 30 \mathrm{lbs}$.\\
c. $\quad 34 \mathrm{lbs}$.\\
d. $\quad 38 \mathrm{lbs}$.\\

\item If you need to feed chlorine at orate of $2.1 \mathrm{mg} / \mathrm{l}$ and you treat $2,300,000$ gallons. How many pounds of chlorine should you use?\\
a. $\quad 4 \mathrm{lbs}$.\\
b. $\quad 17 \mathrm{lbs}$.\\
c. $\quad 35 \mathrm{lbs}$.\\
d. $\quad 40 \mathrm{lbs}$.\\

\item What is the head on a system exerting a static pressure of 62 psi?\\
a. 89 feet\\
b. 107 feet\\
c. 143 feet\\
d. 189 feet \\


\item A head of 200 feet would equal:\\
a. $\quad 46.6 \mathrm{psi}$\\
b. $\quad 56.6 \mathrm{psi}$\\
c. $\quad 66.6 \mathrm{psi}$\\
d. $\quad 86.6 \mathrm{psi}$\\


\item If a 3,000,000 gpd flow is to be dosed with $1.2 \mathrm{mg} / \mathrm{l}$, what should the chlorinator feed rate be set at in lbs. of chlorine per day?\\
a. $\quad 3.0 \mathrm{lbs} . /$ day\\
b. $\quad 4.5$ 1bs./day\\
c. $10 \mathrm{lbs} . /$ day\\
d. $\quad 30 \mathrm{lbs} . /$ day\\

\item Which of the following does not affect the friction loss in a given length of pipe?\\
a. hardness of the water\\
b. number of fittings\\
c. roughness of the interior of the pipe\\
d. velocity of the flow\\

\item Calculate the area in square feet of: a space $100 \mathrm{ft}$ long and $75 \mathrm{ft}$ svide. $100 \times 75$ Ans. TTur Sq. Fr.\\

\item Calculate the volume of a rectangular tank 20 feet high, $100 \mathrm{ft}$ long, and 75 feet wike.\\
Ans. $\frac{10 \text { wo }}{1}$ Cu.Ft.\\

\item Calculate the gallons the tank in the preceding problem will hold. Ans. $1,122,000$ Gallons\\

\item Calculate the area in square feet of a space $40 \mathrm{ft}$ long and 50 feet vvide.\\
Ans, 2000 Sq. Ft\\

\item Calculate the volume of a rectangular tank 40 ft long, 50 ft wide and 25 feet tall.\\
$$\text { Ans. } 50,000 \text { Cu.Ft }$$\\

\item Calculate the gallons the tank in the preceding problem will contain.\\
Ans. 374,000 Gallons\\


\item Calculate the area of a circle with a $10 \mathrm{ft}$ radius.\\
Ans. $314 \quad$ Sq Ft\\

\item Calculate the aren of a circle with a 10 ft diameter.\\
Ans. $78-5$\\

\item Calculate the yolmue of a tank with a 50 ft diameter that is 20 feet high.\\
$$\text { Ans. } 39,260$$Cu. Ft\\

\item How many gallons will the tank in the preceding problem hold?\\

\item Calculate the area of a circle with a 100 ft dibmeter.\\
$$\text { Ans. } 293,590$$\\
Ans. $7,800 \mathrm{Sq} \mathrm{Ft}$\\

\item Calculate the volume of a tank with a $100 \mathrm{ft}$ diameter that is 50 feet high.\\
$$392,500$$\\
Ans.\\

\item How many gallons ryill the tank in the preceding problen hold? Auls.\\
$2,935,960$\\
$$18 \times 18 \times 0^{\prime} 0408 \times 1200$$\\

\item How many gallons will an $18^{\prime \prime}$ diameter pipeline, 1200 ' long contain?\\
$$\text { imi }=5280 \text { Ans. 15,863 Gallons }$$\\

\item How many gallons will a 24 " pipeline, 2 miles long contain?\\
$$24 \times 24 \times 0.0408 \times \quad 248,168$$\\

\item 500 GPM is how many gallons per houl?\\
10560\\
$$\frac{500 \mathrm{~g}^{\prime}}{1 \mathrm{~m}}=\frac{500}{1 / 10 h}=\text { Ans } \frac{30 \text { e0r }}{\mathrm{gph}}$$\\

\item 30,000 gph is how many gallons per day?\\
$$\frac{30,000 \mathrm{~g}}{h}=\frac{30,000}{1 / 24}=30,020 \times 24 \text { Ans. } \frac{720,010}{\mathrm{gpd}}$$\\
\item A flow of $25 \mathrm{gpm}$ is low many gpd?\\
$$\frac{25 \mathrm{~g}}{m}=\frac{25}{1 / 60} \times \frac{1}{24} \quad(25 \times 1440) \text { Ans. } 36,0 w \text { gpd }$$\\

\item A flow of $800,000 \mathrm{gpd}$ is how many gpm? $\frac{800,000}{0.8 M G D \times 700}=560 \times 24 \times 60 \quad 555.55$\\
$0.80 \mathrm{gpm}$\\

\item A flow of $150 \mathrm{gpnn}$ is how many MGD?\\
$$700 \text { (wm. }$$\\
Ans.\\
$\mathrm{MGD}$\\

\item How many gallons will an $8^{\prime \prime}$ pipeline 550 ' long contain?\\
$$8 \times 8 \times 0.0408 \times 550$$\\
Ans. $1436 \cdot \frac{16}{\text { gallons }}$\\

\item Water is filling a tank at the rate of 50 gpm for a 10 min. period, How many gallons of water are contained in the tank at the end of the 10 minute time period?\\

\item A well pump is discharging water at the rate of 400 gpm into a tank for 15 minutes. Haw many gallons will be in the tank at the end of this time period?\\
$$6,000 \ldots \text { Gal. }$$\\
Dose $=$ Dewand T Resrdual $\frac{300}{20} \times 16$\\

\item A tank is filling at the rate of $300 \mathrm{gpm}$ for a 20 minute period. How many of water will be contained in the tank at the end of 16 minutes?\\
4880 Gal.\\

\item Before pumping, the static water level in a well is 15 feet. During pumping, the water lewel drops to 45 feet. What is the drawdown? $45-15=30$\\
a. 15\\
b. 30\\
c. 45\\
d. 60\\
e. 90\\

\item Over a four year period, the hour meter on a electrical panel at a well site had the following readings at the end of each year: $1^{\text {st }}$ year $-976.3,2^{\text {nd }}$ year $-1325.8,3^{\text {rd }}$ year $-2007.1$, and $4^{\text {th }}$ year $-2371.4$. How many hours does the meter show the well ran during the $3^{\text {rd }}$ year?\\
a. $349.5 \mathrm{hrs}$\\
b. $3364.3$ hrs\\
c. $981.3 \mathrm{hrs}$\\
d.  $830.2 \mathrm{hn \prime s}$\\
e. $900.1$\\

\item One gallon of water weighs how many lbs?\\
a. $7.48$\\
b. $8.34$\\
c. $2.31$\\
d. $433 18$.

\item A water tank is filled to depth of 22 feet. What is the psi at the bottom of the tank?\\
$$22 / 2.31 \quad 9.52$$\\

\item The static pressure in a water main is 85 psi. What elevation of water is needed to provide that kind of pressure?\\
$$85 \times 2.31 \quad 196$$\\

\item Calculate the pressure at the bottom of a water tank if it is filled to a depth of 33 feet.\\
$$33 / 2.31$$ft\\

\item A psi gauge is located at the bottom of a water tank and reads 24 psi. What is the elevation of the water inside the tank?\\
$$24 \times 2.31 \quad 55$$\\

\item A gauge is reading the pressure at the outlet of a fire hydrant. A tank is elevated 200 feet above the hydrant. What is the gaige pressure at the hydirant?\\
$$20 s / 2.31$$\\

\item A gauge is attached to a hose bib at a house. The gauge reads $45 p$ ps. How much elevation is needed to supply that pressure?\\
$$45 \times 2.31 \quad 104$$\\

\item How many galtons will the above cylinder hold?\\
$100 \times 7.48=748$\\

\item Calculate the area in square feet of a space $100 \mathrm{ft}$. long and $75 \mathrm{ft}$ widie.\\
Ans. $7500 \quad$ Sq. Fit\\

\item Calculate the volume of a rectangular tank 20 feet high, $100 \mathrm{ft}$ long, and 75 feet wide.\\
Ans. $150,00 \quad$ Cu.F.\\

\item Calculate the gallons the tauk in the preceding problem will hold.\\

\item Calculate the area in square feet of a space $40 \mathrm{ft}$ long and 50 feet wide.\\
Ans, $\frac{2,000}{1}$ Sq. Ft\\

\item Calculate the volume of a rectangular tank $40 \mathrm{ft}$ long, $50 \mathrm{ft}$ wide and 25 feet tall.\\
Ans. $50000 \quad \mathrm{Cu} . \mathrm{Ft}$\\

\item Calculate the gallons the tank in the preceding problem will contain.\\
$$50,000 \times 7.48 \text { Ans. } 374,000 \text { Gallons }$$\\

\item Caiculate the area of a circle with a $10 \mathrm{ft}$ radius.\\
$$D=20 \text {. }$$\\
Ans. $314 \quad \mathrm{Sq} \mathrm{Ft}$\\

\item Calculate the area of a circle with a 10 ft diameter.\\
Ans. $78.5 \quad \mathrm{Sq} \mathrm{Ft}$\\

\item Calculate the volume of a tank with a $50 \mathrm{ft}$ diameter that is 20 feet high.\\
$$\text { Ans. } 250 \quad \mathrm{Cu} \text {. Ft }$$\\

\item How many gallons will the tank in the preceding problem hold?\\

\item Calculate the area of a circle with a $100 \mathrm{ft}$ ciameter.\\
Ans. $\frac{293590}{7850}$ Gallons\\

\item Caiculate the volume of a tank zwith a $100 \mathrm{ft}$ diameter that is 50 feet higl,\\
$$392,50$$\\
$\frac{300 \text { gallons }}{1 \text { mute }} \times 6 \mathrm{~mm}$\\

\item A tank is filling at the rate of $300 \mathrm{gpm}$ for a 20 minute period. How many of water will be contained in the tank at the end of 16 minutes?\\

\item Before pumping, the static water level in a well is 15 feet. During pumping, the water level drops to 45 feet. What is the drawdown?\\
a. 15\\
b. 30\\
c. 45\\
d. 60\\
e. 90\\

\item Over a four year period, the hour meter on a electrical panel at a well site had the following.readings at the end of each year: $1^{\text {sl }}$ year $-976.3,2^{\text {td }}$ year $-1325.8,3^{\text {rd }}$ year $-20071$, and $4^{\text {th }}$ year $-2371$. 4. How many hours does the meter show the well ran during the $3^{\text {rd }}$ year?\\
a. $349.5 \mathrm{hrs}$\\
b. $3364.3$ his\\
c. $\oint 81.3 \mathrm{hrs}$\\
d. $830.2 \mathrm{hrs}$\\
e. $900.1$\\


\item Approximately how many gallons of water can fit into a reservoir that is 35 feet tall and has a 100 foot diameter?\\
a. $2,000,000$\\
b. $2.055 \mathrm{MG}$\\
c. $4 \mathrm{MG}$\\
d. 275,000\\


\item Determine the detention time in hours for the following water treatment system:\\
-	Distribution pipe from water plant to storage tank is 549 ft in length and 14 in. in diameter\\
-	Storage tank averages 2,310,000 gal of water at any given time\\
-	Flow through system is 6.72 mgd\\
a.	7.2 hr\\
b.	7.4 hr\\
c.	8.0 hr\\
d.	8.3 hr\\
\item If chlorine is being fed at a rate of 260 lb/day for a flow rate of 23 cfs, what should be the adjustment on the chlorinator when the flow rate is decreased to 16 cfs, if all other water parameters remain the same?\\
a.	160 lb/day\\
b.	180 lb/day\\
c.	310 lb/day\\
d.	370 lb/day\\
\item How many gallons of a sodium hypochlorite solution that contains 12.1\% available chlorine are needed to disinfect a 1.5-ft diameter pipeline that is 283 ft long, if the dosage required is 50.0 mg/L? Assume the sodium hypochlorite is 9.92 lb/gal.\\
a.	0.87 gal sodium hypochlorite\\
b.	1.0 gal sodium hypochlorite\\
c.	1.3 gal sodium hypochlorite\\
d.	1.5 gal sodium hypochlorite\\
\item A storage tank has a 60.0-ft radius and averages 25.5 ft in water depth. Calculate the average detention time in hours for this storage tank, if flow through the tank averages 2.91 mgd during the month in question.\\
a.	17.5 hr\\
b.	17.8 hr\\
c.	18.6 hr\\
d.	19.8 hr\\
\item A 24.0-in. pipeline, 427 ft long, was disinfected with calcium hypochlorite tablets with 65.0\% available chlorine. Determine the chlorine dosage in mg/L, if 7.0 1b of calcium hypochlorite was used.\\
a.	25 mg/L chlorine\\
b.	39 mg/L chlorine\\
c.	43 mg/L chlorine\\
d.	54 mg/L chlorine\\
\item A well yields 2,840 gallons in exactly 20 minutes. What is the well yield in gpm?\\
a.	140 gpm\\
b.	142 gpm\\
c.	145 gpm\\
d.	150 gpm\\
\item What is the area of a circular tank pad in ft2, if it has a diameter of 102 ft?\\
a.	6,160 ft2\\
b.	6,167 ft2\\
c.	8,170 ft2\\
d.	8,200 ft2\\
\item What is the pressure at 1.85 feet from the bottom of a water storage tank if the water level is 28.7 feet?\\
a.	11.6 psi\\
b.	12.4 psi\\
c.	62.0 psi\\
d.	66.3 psi\\
\item How many gallons are in a pipe that is 18.0 inches in diameter and 1,165 feet long?\\
a.	2,060 gal\\
b.	10,300 gal\\
c.	15,400 gal\\
d.	17,200 gal\\
\item Convert 37.4 degrees Fahrenheit to degrees Celsius.\\
a.	3.0 C\\
b.	5.3 C\\
c.	7.9 C\\
d.	9.7 C\\
\item If 288 is 70.3\%, how much is 100\%?\\
a.	410\\
b.	202\\
c.	218\\
d.	438\\


\item If the pressure head on a fire hydrant is 134 ft, what is the pressure in psi?\\
a.	50 psi\\
b.	52 psi\\
c.	54 psi\\
d.	58 psi\\
\item A meter indicates the water flow from a fire hydrant is 5.5 ft3/min. How many gallons will flow from the hydrant in 20 minutes?\\
a.	820 gal\\
b.	850 gal\\
c.	880 gal\\
d.	920 gal\\
\item Records for a pump show that on June 1 at exactly 9:00 a.m. the number of pumped gallons was 71,576,344 and on July 1 at exactly 9:00 a.m. it was 72,487,008 gallons. Determine the average gallons pumped per day (gal/day) for this month to the nearest gallon.\\
a.	18,605 gal/day\\
b.	25,875 gal/day\\
c.	30,355 gal/day\\
d.	34,325 gal/day\\

\item How much paint will it take for a single coat of the top and sidewalls of the storage tank that is 100-feet in diameter and 30-feet tall, if one gallon of paint covers 200 square feet?\\
a. $\quad 86$ gallons\\
b. $\quad 96$ gallons\\
c. $\quad 106$ gallons\\
d. $\quad 116$ gallons\\
e. $\quad 126$ gallons

\item Under like conditions, how much more water would an 8-inch pipe carry than a 4-inch pipe?\\
a.	2 times\\
b.	3 times\\
c.	4 times\\
d.	not enough information given\\

\item If a lake is 574 feet deep, what is the pressure in pounds per square inch at the bottom of the lake?\\
a. 248 psi\\
b. 1326 psi\\
c. 69 psi\\
d. 62.4 psi\\

\item A pressure gauge reading is 80 psi. How many feet of head is this?\\
A. 173 feet\\
B. 185 feet\\
C. 200 feet\\
D. 212 Feet\\
\item The pump is 150 feet below the reservoir level. What is the pressure reading on the gauge in psi?\\
A. 52 psi\\
B. 60 psi\\
C. 65 psi\\
D. 75 psi\\
\item A tank is 20' x 60' by 15' deep. What is the volume in\\
gallons?\\
A. 115, 000 gallons\\
B. 128,000 gallons\\
C. 135,000 gallons\\
D. 154,000 gallons\\
\item A tank is 60' in diameter and 22' high. How many gallons will it hold?\\
A. 465,000 gallons\\
B. 528,000 gallons\\
C. 640,000 gallons\\
D. 710,000 gallons\\
\item A dosage of 2.4 mg/l of chlorine gas is added to 3.8 mgd. How many pounds per day of chlorine are needed?\\
A. 68 lbs/day\\
B. 76 lbs/day\\
C. 82 lbs/day\\
D. 88 lbs/day\\
\item How many gallons are in a 6" pipe 950 feet long?\\
A. 1108 gallons\\
B. 1253 gallons\\
C. 1308 gallons\\
D. 1395 gallons\\
\item A 12" pipe is carrying water at a velocity of 5.8 fps. What is the flow?\\
A. 4.55 cfs\\
B. 5.36 cfs\\
C. 5.67 cfs\\
D. 6.04 cfs\\
\item The pressure at the top of the hill is 62 psi. The pressure at the bottom of the hill, 60 feet below, is 100 psi. The water is flowing uphill at 120 gpm. What is the friction loss, in feet, in the pipe?\\
A. 24.6 feet\\
B. 27.8 feet\\
C. 31.2 feet\\
D. 33.8 feet\\
\item  A tank is 82' in diameter and 31 feet high. The flow is 1600 gpm. What is the detention time in hours?\\
A. 12.75 hours\\
B. 14.80 hours\\
C. 16.00 hours\\
D. 18.25 hours\\

\item A tank is 120' x 50' x 14' deep. The flow is 2.8 mgd.  What is the detention time in hours?\\
A. 3.8 hours\\
B. 4.4 hours\\
C. 5.3 hours\\
D. 6.2 hours\\

\item A 16" pipe is 1250 feet long. How much 65\% HTH is needed to dose it with 50 mg/l of chlorine?\\
A. 6.50 lbs\\
B. 7.25 lbs\\
C. 7.96 lbs\\
D. 8.34 lbs\\

\item A solution of hydrofluosilisic acid is 22\% fluoride. If 750 ppb are added to 5,600,000 gallons/day, how many ml/min should the pump be feeding?\\
A. 26 ml/min\\
B. 35 ml/min\\
C. 42 ml/min\\
D. 50 ml/min\\

\item A bleach system feeds 12\% bleach. The dosage is 1.4 mg/l for 8.2 mgd. How many ml/min should the pump feed?\\
A. 200 ml/min\\
B. 250 ml/min\\
C. 300 ml/min\\
D. 350 ml/min\\
7. Pump Data:\\

\item Feet - Positive Suction Head\\
158 Feet - Discharge Head\\
26 Feet - Friction Loss\\
1200 gpm - Flow\\
Motor Efficiency - 86\%\\
Pump Efficiency - 78\%\\
What is the motor horsepower?\\
A. 60 MHp\\
B. 65 MHp\\
C. 70 MHp\\
D. 75 MHp\\

\item Pump Data:\\
20 Feet - Positive Suction Head\\
185 Feet - Discharge Head\\
18 Feet - Friction Loss\\
300 gpm - Flow\\
Motor Efficiency - 90\%\\
Pump Efficiency - 80\%\\
Kw-Hour Cost = 0.11/Kw-Hr\\
Average Run Time – 6 Hours/day\\
What is the cost to run the pump for 30 days?\\
A. \$245.08\\
B. \$284.34\\
C. \$410.50\\
D. \$463.82\\


\item Determine the drawdown from a well measuring a static water level of 120 feet and a pumping water level of 205 feet?\\
a. 105 ft\\
b. 320 feet\\
c. 85 feet\\
d. 310 feet\\

\item Before pumping, the static water level in a well is 15 feet. During pumping, the water level drops to 45 feet. What is the drawdown?\\
a. 15 ft\\
b. 30 ft\\
c. 45 ft\\
d. 60 ft\\
e. 90 ft\\

\item What is the chlorine demand of a tank that is dosed at 3.5 ppm and has a residual of 1.25 ppm.\\
a. 2.25 \\
b. 4.75 \\
c. 1.25 \\
d. 3.5 \\
e. not enough information\\
\item What 1s the area of a trench that is 22.4 ft Jong and 3 .3 feet wide?\\
a. 26 sq.ft\\
b. 74 sq. ft.\\
c. 143 sq. ft\\
d. 187 sq. ft.\\
\item What is the pounds per square inch pressure at the bottom ofa tank if the water level is 38.29 feet?\\
a. 7.3 psi\\
b. 16.6 psi\\
c. 53.9 psi \\
d. 88.4 psi\\
\item What is the pressure head on a system exerting a static pressm·e of 62 psi?\\
a.27 ft\\
b. 89 ft\\
c. 143 ft\\
d. 175 ft\\
\item How many gallons are in a pipe that is 18" in diameterand 216 feet long?\\
a.1908 gallons\\
b. 2246 gallons\\
c. 2430 gallons \\
d. 2861 gallons\\
\item How many pounds of chlorine are required to u·eat 8.65 mgd if the dosage is 2.75 ppm?\\
a. 11 lb/day\\
b. 24 lb/day\\
c. 72 lb/day\\
d. 198 lb/day\\
\item What should the setting be on a chlorinator in pounds per day if the dosage desired is 2.9 mg/l and the pumping rate from the well is 975 gpm?\\
a. 29 lb/day\\
b. 34 lb/day\\
c. 41 lb/day\\
d. 336 lb/day\\
\item What is the chlorine residual in a system that bas a chlorine dosage of2.75 mg/1 and a chlorine demand\\
of 1.93 mg!l?\\
a. 0.82 mg/l\\
b. 1.75 mg/l\\
c. 4.67 mg/l\\
d. 5.3 l mg/l\\
\item How many pounds per day of chlorine are needed to treat 38.75 mgd if the residual is 2.0 mg/1 and the demand is 1.5 mg/l?\\
a. 42 lb/day \\
b. 136 lb/day \\
c. 323 lb/day\\
d. 1131 lb/day\\
\item A pump discharges 680 gpm, How many gallons will it discharge in 8 hours?\\
a. 5440 gallons. \\
b. 130560 gallons\\
c. 1 ac-ft\\
d. 408000 gallons.\\
\item How many gallons are contained in 2167 cu.ft?\\
a. 260 gallons \\
b. 295 gallons\\
c. 16253 gallons\\
d. 18070 gallons\\
\item What is the typical strength of calcium hypochlorite, i.e., available chlorine range?\\
a. 5 to 10\%\\
b. 45 to 50\%\\
c. 65 to 70\%\\
d. 80 to 85\%\\
\item A four log removal is\\
a. 90.00\%\\
b. 99.00\%\\
c. 99.90\%\\
d. 99.99\%\\
\item A circular clearwell is 150 feet in diameter and 40 feet tall. The Clearwell has an overflow at 35 feet. What is the maximum amount of water the clearwell can hold in Million gallons rounded to the nearest hundredth?\\
a. 0.92 MG\\
b. 4.62 MG\\
c. 18.50 MG\\
d. 7.50 MG\\
\item A sedimentation basin is 400 feet length, 50 feet in width, and 15 feet deep. What is the volume expressed in cubic feet?\\
a. 100,000 ft$^3$\\
b. 200,000 ft$^3$\\
c. 300,000 ft$^3$\\
d. 400,000 ft$^3$\\
\item A clearwell holds 314,000 ft³ of water. It is 100 ft in diameter. What is the height of the clearwell?\\
a. 25 ft\\
b. 30 ft\\
c. 35 ft\\
d. 40 ft\\
\item A treatment plant operator must fill a clearwell with 10,000 ft3 of water in 90 minutes. What is the rate of flow expressed in GPM?\\
a. 111 GPM\\
b. 831 GPM\\
c. 181 GPM\\
d. 900 GPM\\
\item A water tank has a capacity of 6MG. It is currently half full. It will take 6 hours to fill. What is the flow rate of the pump?\\
a. 3,333 GPM\\
b. 6,333 GPM\\
c. 8,333 GPM\\
d. 16,666 GPM\\
\item A clearwell with the capacity of 2.5 MG is being filled after a maintenance period. The flow rate is 2,500 GPM. The operator begins filling at 7 AM. At what time will the clearwell be full?\\
a. 10:00 PM\\
b. 10:40 PM\\
c. 11:00 PM\\
d. 11:40 PM\\
\item There are four filters at a water treatment plant. The filters measure 20 feet wide by 30 feet in length. What is the filtration rate if the plant processes 8.0 MGD?\\
a. 1.51 GPM/sq.ft.\\
b. 2.31 GPM/sq.ft.\\
c. 2.61 GPM/sq.ft.\\
d. 2.91 GPM/sq.ft.\\
\item A water treatment plant treats 6.0 MGD with four filters. The filters use 60,000 gallons per wash. What is the percent backwash at the plant?\\
a. 10 \%\\
b. 8 \%\\
c. 6\%\\
d. 4\%\\
\item A treatment plant filter washes at a rate of 10,000 GPM. The filter measures 18ft. wide by 24ft. long. What is the rate of rise expressed in inches per minute?\\
a. 17 inch/min\\
b. 27 inch/min\\
c. 37 inch/min\\
d. 47 inch/min\\


\end{enumerate}
\end{document}