\documentclass{article}


\usepackage{verbatim}


\usepackage{tocloft}


\usepackage{graphicx} % Required for including pictures
\graphicspath{{Pictures/}} % Specifies the directory where pictures are stored

\usepackage{lipsum} % Inserts dummy text

\usepackage{tikz} % Required for drawing custom shapes

\usepackage[english]{babel} % English language/hyphenation

\usepackage[shortlabels]{enumitem}


% \usepackage{enumitem} % Customize lists
\setlist{nolistsep} % Reduce spacing between bullet points and numbered lists

\usepackage{booktabs} % Required for nicer horizontal rules in tables

\usepackage{xcolor} % Required for specifying colors by name
\definecolor{ocre}{RGB}{243,102,25}
\definecolor{golden}{RGB}{252, 29, 3}

 % Define the orange color used for highlighting throughout the book

%----------------------------------------------------------------------------------------
%	MARGINS
%----------------------------------------------------------------------------------------

\usepackage{geometry} % Required for adjusting page dimensions and margins

\geometry{
	paper=a4paper, % Paper size, change to letterpaper for US letter size
	top=3cm, % Top margin
	bottom=3cm, % Bottom margin
	left=3cm, % Left margin
	right=3cm, % Right margin
	headheight=14pt, % Header height
	footskip=1.4cm, % Space from the bottom margin to the baseline of the footer
	headsep=10pt, % Space from the top margin to the baseline of the header
	%showframe, % Uncomment to show how the type block is set on the page
}




\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage[english]{babel}
\usepackage{graphicx}
\usepackage{tabulary}
\usepackage{tabularx}
\usepackage{cancel}
\usepackage{pagecolor}
\usepackage{afterpage}
\usepackage{soul}
\usepackage{fixltx2e}
\usepackage[utf8]{inputenc}
\usepackage{siunitx} %degrees for Laboratory
\usepackage{pdflscape} %sidescape figure in Laboratory
\usepackage{float}
\usepackage{xcolor}
\usepackage{framed}
\usepackage{mdframed}
\usepackage{soul}
%\textsubscript{this}
\usepackage{lastpage}
\usepackage[utf8]{inputenc}
\usepackage{ifthen}
\usepackage{amsmath}
\usepackage{fancyhdr}
\usepackage[document]{ragged2e}
% \usepackage[margin=1in,top=1.2in,headheight=57pt,headsep=0.1in]{geometry}
\usepackage{fancyhdr}
\usepackage{caption}
\usepackage{subcaption}
%Chapter 2
\usetikzlibrary{calc}
\usetikzlibrary{arrows}
\usepackage{rotating}%for sidewaysfigure
\usepackage[final]{pdfpages}
\usepackage{tcolorbox}
%\usepackage[dvipsnames]{xcolor}
\usepackage{colortbl}
\usepackage{chemfig}
\usepackage{lscape}
\usepackage{wrapfig}
\usepackage[final]{pdfpages}
\usepackage{setspace}
%\usepackage[table]{xcolor}
%----------------------------------------------------------------------------------------
%	FONTS
%----------------------------------------------------------------------------------------

\usepackage{avant} % Use the Avantgarde font for headings
%\usepackage{times} % Use the Times font for headings
\usepackage{mathptmx} % Use the Adobe Times Roman as the default text font together with math symbols from the Sym­bol, Chancery and Com­puter Modern fonts

\usepackage{microtype} % Slightly tweak font spacing for aesthetics
\usepackage[utf8]{inputenc} % Required for including letters with accents
\usepackage[T1]{fontenc} % Use 8-bit encoding that has 256 glyphs

%----------------------------------------------------------------------------------------
%	BIBLIOGRAPHY AND INDEX
%----------------------------------------------------------------------------------------

\usepackage[style=numeric,citestyle=numeric,sorting=nyt,sortcites=true,autopunct=true,babel=hyphen,hyperref=true,abbreviate=false,backref=true,backend=biber]{biblatex}
\addbibresource{bibliography.bib} % BibTeX bibliography file
\defbibheading{bibempty}{}

\usepackage{calc} % For simpler calculation - used for spacing the index letter headings correctly
\usepackage{makeidx} % Required to make an index
\makeindex % Tells LaTeX to create the files required for indexing



%----------------------------------------------------------------------------------------
%	MAIN TABLE OF CONTENTS
%----------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------
%	MAIN TABLE OF CONTENTS
%----------------------------------------------------------------------------------------

\usepackage{titletoc} % Required for manipulating the table of contents

\contentsmargin{0cm} % Removes the default margin

% Part text styling (this is mostly taken care of in the PART HEADINGS section of this file)
\titlecontents{part}
	[0cm] % Left indentation
	{\addvspace{20pt}\bfseries} % Spacing and font options for parts
	{}
	{}
	{}

% Chapter text styling
\titlecontents{chapter}
	[1.25cm] % Left indentation
	{\addvspace{12pt}\large\sffamily\bfseries} % Spacing and font options for chapters
	{\color{ocre!60}\contentslabel[\Large\thecontentslabel]{1.25cm}\color{ocre}} % Formatting of numbered sections of this type
	{\color{ocre}} % Formatting of numberless sections of this type
	{\color{ocre!60}\normalsize\;\titlerule*[.5pc]{.}\;\thecontentspage} % Formatting of the filler to the right of the heading and the page number

% Section text styling
\titlecontents{section}
	[1.25cm] % Left indentation
	{\addvspace{3pt}\sffamily\bfseries} % Spacing and font options for sections
	{\contentslabel[\thecontentslabel]{1.25cm}} % Formatting of numbered sections of this type
	{} % Formatting of numberless sections of this type
	{\hfill\color{black}\thecontentspage} % Formatting of the filler to the right of the heading and the page number

% Subsection text styling
\titlecontents{subsection}
	[1.25cm] % Left indentation
	{\addvspace{1pt}\sffamily\color{golden}} % Spacing and font options for subsections
	{\contentslabel[\thecontentslabel]{1.25cm}} % Formatting of numbered sections of this type
	{} % Formatting of numberless sections of this type
	{\ \titlerule*[.5pc]{.}\;\thecontentspage} % Formatting of the filler to the right of the heading and the page number
	
% Subsection text styling
\titlecontents{subsubsection}
	[1.25cm] % Left indentation
	{\addvspace{1pt}\sffamily\color{ocre}} % Spacing and font options for subsections
	{\contentslabel[\thecontentslabel]{1.25cm}} % Formatting of numbered sections of this type
	{} % Formatting of numberless sections of this type
	{\ \titlerule*[.5pc]{.}\;\thecontentspage} % Formatting of the filler to the right of the heading and the page number

% Figure text styling
\titlecontents{figure}
	[1.25cm] % Left indentation
	{\addvspace{1pt}\sffamily\small} % Spacing and font options for figures
	{\thecontentslabel\hspace*{1em}} % Formatting of numbered sections of this type
	{} % Formatting of numberless sections of this type
	{\ \titlerule*[.5pc]{.}\;\thecontentspage} % Formatting of the filler to the right of the heading and the page number

% Table text styling
\titlecontents{table}
	[1.25cm] % Left indentation
	{\addvspace{1pt}\sffamily\small} % Spacing and font options for tables
	{\thecontentslabel\hspace*{1em}} % Formatting of numbered sections of this type
	{} % Formatting of numberless sections of this type
	{\ \titlerule*[.5pc]{.}\;\thecontentspage} % Formatting of the filler to the right of the heading and the page number
















































%\usepackage{tikz}
%\usepackage[utf8]{inputenc}
%\usepackage{graphicx}
%\usepackage{fancyhdr}
%\usepackage{microtype}
%\usepackage{geometry}
%\usepackage{xcolor} % Required for specifying colors by name
%\definecolor{ocre}{RGB}{243,102,25} % Define the orange color used for highlighting throughout the book
%
%
%\usepackage{amsfonts, amsmath, amssymb, amsthm}
%\usepackage[T1]{fontenc}
%



\begin{document}
Water Facts - Worldwide Water Supply
Water covers about 71% of the earth's surface.
326 million cubic miles of water on the planet
97% of the earth's water is found in the oceans (too salty for drinking, growing crops, and most industrial uses except cooling).
320 million cubic miles of water in the oceans
3% of the earth's water is fresh.
2.5% of the earth's fresh water is unavailable: locked up in glaciers, polar ice caps, atmosphere, and soil; highly polluted; or lies too far under the earth's surface to be extracted at an affordable cost.
0.5% of the earth's water is available fresh water.
If the world's water supply were only 100 liters (26 gallons), our usable water supply of fresh water would be only about 0.003 liter (one-half teaspoon).
In actuality, that amounts to an average of 8.4 million liters (2.2 million gallons) for each person on earth.
This supply is continually collected, purified, and distributed in the natural hydrologic (water) cycle.
Where Water is Found and the Percentage
Oceans	97.2%
Ice Caps/Glaciers	2.0%
Groundwater*	0.62%
Freshwater Lakes	0.009%
Inland seas/salt lakes	0.008%
Atmosphere	0.001%
Rivers	0.0001%
TOTAL	99.8381%
If the Earth Were a Globe 28 Inches in Diameter:

All of the water on the planet would fill less than one cup.
Only 0.03% of one cup is in rivers and fresh water lakes.
Slightly more than one drop of water would fill all the rivers and lakes.
If 5 Gallons Represents all the Water on Earth (in tablespoons):
Oceans	1244.16
Ice Caps/Glaciers	5.60
Groundwater*	7.93
Freshwater Lakes	0.11
Inland seas/salt lakes	0.10
Atmosphere	0.0128
Rivers	0.0012
TOTAL	1277.9130
*Some of this lies too far under the earth's surface to be extracted at an affordable cost

Sources of Fresh Water

Groundwater - water which infiltrates into the ground through porous materials deeper into the earth. It fills pores and fractures in layers of underground rock called aquifers. Some of this water lies too far under the earth's surface to be extracted at an affordable cost.
Surface-water runoff - precipitation that does not infiltrate into the ground or return to the atmosphere: streams, rivers, lakes, wetlands, and reservoirs.
Snow that is 4 inches (10cm) deep contains about the same amount of water as 1/3 inch (1 cm) of rain.
Water Use in the U.S.

8% domestic use
33% agriculture
59% industry
Over 600 gallons per day per person in the U.S. is being diverted for farm irrigation and livestock use from natural aquatic sources.
More than half the people in the U.S. get their water from groundwater.
Measures of Water Use

Water withdrawal - taking water from groundwater or surface-water source and transporting it to a place of use.
Water consumption - water that has been withdrawn and is not available for reuse in the area from which it is withdrawn.
In the U.S. about three-fourths of the fresh water withdrawn each year comes from rivers, lakes and reservoirs; one-fourth comes from groundwater aquifers.
80% of water withdrawn in the U.S. is used for cooling electric power plants and for irrigation.
Home Water Use (Approximate)
Gallons	Activity
3	Shaving and allowing the water faucet to run
1.6-5	Flushing a toilet
5	Brushing your teeth and allowing the water faucet to run
8	Cooking 3 meals
8	Cleaning house
10	Washing dishes for 3 meals
20-30	Washing clothes
30	Washing dishes and allowing the water faucet to r
30-40	Watering lawn
30-40	Washing a car
30-40	Taking a bath
40	8 minute shower (5 gallons/minute
A leak that fills up a coffee cup in 10 minutes will waste over 3,000 gallons of water in a year. That's 65 glasses of water every day for a year.
A leaky toilet can waste over 22,000 gallons of water in one year; enough to take three baths every day
Garden Water Use

Americans use about 1/3 more water in the summer than they do the rest of the year because they're watering their lawns.
There are about 10 million acres of lawn in the U.S., which requires 270 billion gallons of water every week. That's enough to give every person in the world a shower for four days in a row.
Most lawns only need an inch of water each week.
Water in the Body

Eye - 95% water
Total body weight - 75% water
How Much Water Does it Take to Produce Your Food?
Food	Portion	Gallons of Water
Orange Juice	1 cup	49
Orange	1 medium	14
Cantaloupe	1 melon	160
Broccoli	2 cups	11
Catsup	1 ounce	3
Corn	1 ear	80
Lettuce	1 cup	3
Tomato	1 small	8
Tomato Sauce	4 ounces	13
Butter	1 pat	46
Cheese	1 ounce	56
Milk	1 cup	48
Yogurt	1 cup	88
Beef Steak	8 ounces	1,232
Chicken	8 ounces	330
Egg	1 each	50
Hamburger	4 ounces	616
Tofu	2 cups	61
Almonds	1 ounce	80
Sugar	1 Tablespoon	7
White Rice	2 cups	25
Brown Rice	2 cups	16
Wheat Bread	1 slice	7
White Bread	1 slice	11
Pasta	2 ounces	36
Water Pollution

A gallon of paint or a quart of motor oil can seep into the earth and pollute 250,000 gallons of drinking water.
A spilled gallon of gasoline can pollute 750,000 gallons of water.
Sources

Aquatic Project WILD; Western Regional Environmental Education Council
Flying Start Science-Water; Kim Taylor
Folsom Dam Fact Sheets; Bureau of Reclamation
Layperson's Guide to The American River; Water Education Foundation
Living in the Environment, An Introduction to Environmental Science; G. Tyler Miller Jr.
Water Facts; Water Education Foundation
50 Simple Things Kids Can Do To Save The Earth; The EarthWorks Group


\end{document}
